\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-07 casestudies.tex
justify escape hatch

Elimination of inductive types defined via \lsti{FInductive} is
mostly via the \lsti{FRecursion} and \lsti{FInduction} commands.
An exception is some seemingly trivial ``inversion lemmas''.
For example, consider the lemma \lsti!\forall t, \neg step tm_true t!
stating that \lsti!tm_true! is irreducible.
If \lsti{step} were an ordinary inductive type, then it could be proved in Coq
with \lsti{intros t H; inversion H}.
But since \lsti{step} is extensible, it seems that the lemma has to be
proved by \lsti{FInduction} on \lsti{step}, and that the programmer
has to manually verify that the lemma still holds in derived families
that add new constructors to \lsti{step}.
%
However, we observe that it is lighter-weight to use overriding (\cref{sec:override}):
the programmer can specify that the proof of the lemma should be overridden
in any derived family that further binds \lsti{step},
and in return, they are permitted to treat \lsti{step} as an ordinary
inductive type in the proof and thus discharge the proof with \lsti{inversion}.
The plugin then automatically tries the same proof script in a derived
family to override the proof.

>>>>

Elimination of inductive types defined via \lsti{FInductive} is
mostly via the \lsti{FRecursion} and \lsti{FInduction} commands.
An exception is a handful of trivial ``inversion lemmas''.
For example, consider the lemma \lsti!\forall t, \neg step tm_true t!
stating that \lsti!tm_true! is irreducible.
If \lsti{step} were an ordinary inductive type, then it could be proved in Coq
simply by \lsti{intros t H; inversion H}.
But since \lsti{step} is extensible, it seems that the lemma has to be
proved by \lsti{FInduction} on \lsti{step}, and that the programmer
has to verify that the lemma still holds in derived families
that add new constructors to \lsti{step}.
%
We observe that it is lighter-weight to use overriding (\cref{sec:override}) instead:
the programmer can specify that the proof of the lemma should be overridden
in any derived family that further binds \lsti{step},
and in return, they are permitted to treat \lsti{step} as an ordinary
inductive type in the proof and thus discharge the proof with \lsti{inversion}.
The plugin then automatically tries the same proof script in a derived
family to override the proof. Although proof scripts rather
than proof terms are reused, rechecking of proof terms seems justified
by the triviality of the lemmas and the terseness of the proofs.
